Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering Input Images

### 2014-12-30 submit/ms.tex
Cleaning up sentences in the discussion section

We describe an end--to--end test suite to optimize the quality of a PSF--matching solution for image subtraction.
The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
This test suite is designed to optimize an objective function, which is the number of false postigive--going and negative--going detections in the subtractions.
We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interolated to their location using a spatial model.

@@

\item At the 5--sigma detection threshold, for the range of seeings
  considered in this production, the theoretical rate of false
  detections per 4k x 4k sensor numbers 3--12, depending on seeing.
  {\bf We are able to realize this theoretical floor}.  This function
  is steep and seeing dependent; by increasing the detection threshold
  to 5.5 sigma this number may be lowered to less than 1 per sensor
  down to seeing of 0.6'' (Table~\ref{tab-fp}).  This translates to of
  order 2 * $10^5$ per night, assuming 1000 visits / night.  The
  steepness of the false positive function will enable control of the
  number of false alerts by small modifications of the detection
  threshold.

@@

\item When strongly deconvolving, the post--filtered variance is 70\%
  {\it higher} at the time of detection compared to the pre--filtered
  data (Table~\ref{tab-variance2}).  This is consistent with the
  understanding that deconvolution increases high frequency noise in
  the images, and provides a {\it lower} detection efficiency in
  deconvolved data.  Pre--filtering is clearly preferred to post--filtering 
  in the case of significant deconvolution (v6866601).

\item For non--deconvolved image subtraction, pre--filtering performs as
  well as post--filtering in terms of the number of false positives, when 
  corrected for the variance underestimate (Figure~\ref{fig:4}).

\item An empirical computation of the variance from the image plane,
  compared to the median propagated variance in the variance plane,
  indicates that we consistently underestimate the variance in
  pre--filtering by $1-2\%$, and in post--filtering by $4-5\%$ when not
  strongly deconvolving (Table~\ref{tab-variance1}).  The post--filtering
  issue is shown to arise from the PSF--filtering of the difference
  image immediately before detection.  This is due, at least in part, to the
  double--convolution that is happening to the template image, and our
  lack of covariance tracking. The dependence on template noise and
  the number of convolutions will impact the requirements on the
  variance within the template images (and thereby the number of
  images going into a template image).

@@

\item The post--filter pipeline can produce difference images with a
  minor deconvolution (v6866602) at a quality commensurate with a subtraction that uses a
  smoothing convolution (v6866603).

@@

\item We find that the overall number of false detections is not
  strongly sensitive to bulk background misestimation
  (Figure~\ref{fig:2});

@@

\item The measured false detection rate is seen to scale with detection
  threshold in a manner consistent with theory (Figure~\ref{fig:4}).
  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships
  into almost exact correspondence.  Optimization of the false detection vs. true source
  detection efficiency will require an understanding of the variance at the 1\% level.

>>>>

We describe an end--to--end test suite to optimize the quality of a PSF--matching solution for image subtraction.
The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
This test suite is designed to optimize an objective function, which is the number of false positive--going and negative--going detections in the subtractions.
We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interpolated to their location using a spatial model.

@@

\item At the 5--sigma detection threshold, for the range of seeings considered in this production, the theoretical rate of false detections per 4k x 4k sensor numbers 3--12, depending on seeing.
  {\bf We are able to realize this theoretical floor}.
  This function is steep and seeing dependent; by increasing the detection threshold to 5.5 sigma this number may be lowered to less than 1 per sensor down to seeings of 0.6'' (Table~\ref{tab-fp}).
  This translates to of order 2 * $10^5$ per night for LSST, assuming 1000 visits / night.
  The steepness of the false detection function will enable control of the number of statistical false alerts by small modifications of the detection threshold.

@@

\item When strongly deconvolving, the post--filtered variance is 70\% {\it higher} at the time of detection compared to the pre--filtered data (Table~\ref{tab-variance2}).
  This is consistent with the understanding that deconvolution increases high frequency noise in the images, and yields a {\it lowered} detection efficiency for true variability in deconvolved data.
  Systematic ringing features around sources also yield an enhanced rate of systematic false detections in deconvolved images.
  For this reason, pre--filtering is clearly preferred to post--filtering in the case of significant deconvolution.

\item For non--deconvolved image subtraction, pre--filtering performs as well as post--filtering in terms of the number of false detections, when corrected for variance underestimate (Figure~\ref{fig:4}).

\item An empirical computation of the variance from the image plane, compared to the median propagated variance in the variance plane, indicates that the software consistently underestimate the variance in pre--filtering by $1-2\%$, and in post--filtering by $4-5\%$ (when not strongly deconvolving; Table~\ref{tab-variance1}).
  The post--filtering discrepancy is shown to arise from the PSF--filtering of the difference image immediately before detection.
  This is likely due, at least in part, to the double--convolution that is happening to the template image, and the lack of covariance tracking within the software.

@@

\item The post--filter pipeline can produce difference images with a minor deconvolution ({\tt visit 2}) at a quality commensurate with a subtraction that uses a smoothing convolution ({\tt visit 3}).

@@

\item We find that the overall number of false detections is not strongly sensitive to bulk background misestimation (Figure~\ref{fig:2}).

@@

\item The measured false detection rate is seen to scale with detection threshold in a manner consistent with theory (Figure~\ref{fig:4}).
  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships into almost exact correspondence.
  Optimization of the false detection vs. true source detection efficiency will require an empirical understanding of the variance at the 1\% level.
